### 2016-08-10 main.tex
Minor word choice change in Accuracies results.

Accuracies for our six test syllables are shown in
\fig{fig:accuracies} (accuracies for the synthetic $\delta$-function
songs were always 100\%).  For each test syllable we trained
100 different
networks, which differ from each other in the random initialisation of
network weights and on which random subset of our songs was used for
training.  Each network's accuracy is shown as a single point in each
chart in \fig{fig:accuracies}, and the means are shown in Table~\ref{table:accuracies}.  Some syllables are easier to identify
reliably than others, showing that detection point choice can impact the
detector's accuracy.  As can be seen from \fig{fig:accuracies}, for difficult syllables, the training process
occasionally yields a network that performs unusually poorly, but it
is easy to spot these networks by their performance either as measured
as part of the training process or on the test audio file, and
re-train when necessary.

>>>>

Accuracies for our six test syllables are shown in
\fig{fig:accuracies} (accuracies for the synthetic $\delta$-function
songs were always 100\%).  For each test syllable we trained
100 different
networks, which differ from each other in the random initialisation of
network weights and on which random subset of our songs was used for
training.  Each network's accuracy is shown as a single point in each
chart in \fig{fig:accuracies}, and the means are shown in Table~\ref{table:accuracies}.  Evidently some syllables are easier to identify
reliably than others; thus, if the experimental design permits, it can be worthwhile to choose an easily identifiable syllable.  Furthermore, as can be seen from \fig{fig:accuracies}, for difficult syllables the training process
occasionally yields a network that performs unusually poorly.  It
is easy to spot these networks by their performance either as measured
as part of the training process or on the test audio file, and
re-train when necessary.
